Supplementary Information

### 2021-08-30 doc/manuscript/ForestGEO_treerings.Rmd
Update ForestGEO_treerings.Rmd

Our process identified similar primary climate drivers to those identified via established dendrochronological analysis methods for identifying climate signals (Figs. `r SCBI_example`, `r all_traditional_comparisons`; Table `r qualitative_results_comparison`; Appendix `r traditional_comparison`).
While one-to-one correspondence of estimated slope coefficients describing the response of tree growth to interannual climatic variation was neither expected nor observed, estimates obtained using the two methods were correlated and rarely differed significantly from one another (Appendix `r traditional_comparison`; `r all_traditional_comparisons`).

@@

![**Figure 2 | Example comparison of climate sensitivity derived via traditional methods (**a**) and our approach (**b-f**).** Example is for the sensitivity of 14 species at SCBI (codes given in Table `r species_table`) to potential evapotranspiration (PET). Panel (**a**) shows a matrix of Pearson correlations between ring-width index and monthly climate variables [produced using the bootRes package in R, @zang_dendroclimatic_2013]. Black rectangle represents the period selected by *climwin* as the most influential window. Panels (**b-d**) give statistics for seasonal windows tested in *climwin*, where window open and close refer to the start- and end-months of the window tested, expressed as months prior to current August, and cells across the lower diagonal indicate single-month tests (akin to panel **a**). Panels (**b**) and (**c**) give values of linear and quadratic terms for each seasonal window, and (**d**) gives the $\Delta$AIC for each. The seasonal window with the minimum $\Delta$AIC (1-3 months prior to August, or May-July; black circles), was identified as the most influential window. Panel (**e**) shows the correlation of individual-level residuals to PET, with the function fit in *climwin*. Finally, panel (**f**) shows the GLS model output, where PET was a candidate driver variable (along with PPT; DBH not included in this model). Plotted are responses of species for which PET was included in the top model, with best-fit polynomials plotted with solid lines when both first- and second-order terms are significant, dash-dotted lines when only one term is significant, and dotted lines when neither is significant. Transparent ribbons indicate 95% confidence intervals. Species names corresponding to the codes are given in Table `r species_table`.](tables_figures/quilt_comparison.png)

>>>>

Our process identified similar primary climate drivers to those identified via established dendrochronological analysis methods for identifying climate signals (Figs. `r SCBI_example`, `r all_traditional_comparisons`; Table `r qualitative_results_comparison`; Appendix `r traditional_comparison`).
While one-to-one correspondence of estimated slope coefficients describing the response of tree growth to interannual climatic variation was neither expected nor observed, estimates obtained using the two methods were correlated and rarely differed significantly from one another (Appendix `r traditional_comparison`; Figs. `r all_traditional_comparisons`).

@@

![**Figure 2 | Example comparison of climate sensitivity derived via traditional methods (**a**) and our approach (**b-f**).** Example is for the sensitivity of 14 species at SCBI (species codes given in Table `r species_table`) to potential evapotranspiration (PET). Panel (**a**) shows a matrix of Pearson correlations between ring-width index and monthly climate variables [produced using the bootRes package in R, @zang_dendroclimatic_2013]. Black rectangle represents the period selected by *climwin* as the most influential window. Panels (**b-d**) give statistics for seasonal windows tested in *climwin*, where window open and close refer to the start- and end-months of the window tested, expressed as months prior to current August, and cells across the lower diagonal indicate single-month tests (akin to panel **a**). Panels (**b**) and (**c**) give values of linear and quadratic terms for each seasonal window, and (**d**) gives the $\Delta$AIC for each. The seasonal window with the minimum $\Delta$AIC (1-3 months prior to August, or May-July; black circles), was identified as the most influential window. Panel (**e**) shows the correlation of individual-level residuals to PET, with the function fit in *climwin*. Finally, panel (**f**) shows the generalized least squares (GLS) model output, where PET was a candidate driver variable (along with PPT; DBH not included in this model). Plotted are responses of species for which PET was included in the top model, with best-fit polynomials plotted with solid lines when both first- and second-order terms are significant, dash-dotted lines when only one term is significant, and dotted lines when neither is significant. Transparent ribbons indicate 95% confidence intervals. Species names corresponding to the codes are given in Table `r species_table`.](tables_figures/quilt_comparison.png)
